---
title: "Monitoring Progress"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    runtime: shiny 
    theme: flatly
---

<style> 
.navbar {
  background-color: #e87d81; 
}
</style> 

```{r setup, include=FALSE}
# Where required install, or load packages, for running the dashboard
require(flexdashboard)
require(shiny)
require(readxl)
require(plyr)
require(dplyr)
require(tidyverse)
require(magrittr)
require(knitr)
require(DT)
require(ggplot2)
require(plotly)
require(networkD3)
require(d3Network)
require(treemap)
require(d3Tree)
require(dygraphs)
require(sys)
require(highcharter)

options(scipen=999)

```

Scorecard {data-orientation=columns}
=======================================================================

Column {style="height:100pc;"}
-----------------------------------------------------------------------

```{r loade, include=FALSE}
# these computing functions are only toy examples
computeArticles = function(...) return(45)
computeComments = function(...) return(126)
computeSpam = function(...) return(15)

RMC <- read_excel("data.xlsx", sheet = "RMC") %>% 
  gather(Type, Quantity, - Date)

RMCmaxval <- ceiling(max(RMC$Date, na.rm = TRUE))
RMCpen <- ceiling(max(RMC$Date, na.rm = TRUE)-1)

```

### Raw Material Consumption `r RMCpen` - `r RMCmaxval`

```{r}
RMClatest <- read_excel("data.xlsx", sheet = "RMC") %>% 
  gather(Type, Quantity, - Date) %>% filter(Type=="Material_Footprint")

RMCa <- with(RMClatest, Quantity[which.max(Date)])
RMCb <- with(RMClatest, Quantity[which.max(Date)-1])
RMCc <- (RMCa/RMCb-1)*100
RMCc <- round(RMCc, digits = 2)

articlesa = RMCc
valueBox(paste0(articlesa,"%"), icon = "fa-road",
         color = ifelse(articlesa > 0, "warning", "primary"))

```

### Resource Productivity `r RMCpen` - `r RMCmaxval`

```{r}
target3 <- c("Oresrp", "BiomassMaterialsrp", "FossilFuelsrp", "Mineralsrp", "Material_Footprintrp")

RMCrplatest <- 
  read_excel("data.xlsx", sheet = "RMC") %>%
  mutate(Oresrp = GDP/(Ore_Materials*1000000)) %>%
  mutate(BiomassMaterialsrp = GDP/(Biomass_Materials*1000000)) %>%
  mutate(FossilFuelsrp = GDP/(Fossil_Fuels*1000000)) %>%
  mutate(Mineralsrp = GDP/(NMMM*1000000)) %>% 
  mutate(Material_Footprintrp = GDP/(Material_Footprint*1000000)) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% target3) 

RMCrpa <- with(RMCrplatest, Quantity[which.max(Date)])
RMCrpb <- with(RMCrplatest, Quantity[which.max(Date)-1])
RMCrpc <- (RMCrpa/RMCrpb-1)*100
RMCrpc <- round(RMCrpc, digits = 2)

articles = RMCrpc
valueBox(paste0(articles,"%"), icon = "fa-road",
         color = ifelse(articles > 0, "olive", "primary"))

```

### Carbon Footprint

```{r}
comments = computeComments()
valueBox(comments, icon = "fa-fire")
```

### Waste Sector Emissions

```{r}
comments = computeComments()
valueBox(comments, icon = "fa-fire")
```

Column {style="height:100pc;"}
-----------------------------------------------------------------------

### Total Waste Arisings

```{r}
spam = computeSpam()
valueBox(
  spam, icon = "fa-trash",
  color = ifelse(spam > 10, "warning", "primary")
)
```    

### Household Arisings

```{r}
spam = computeSpam()
valueBox(
  spam, icon = "fa-trash",
  color = ifelse(spam > 10, "warning", "primary")
)
```    

### C&I Arisings

```{r}
spam = computeSpam()
valueBox(
  spam, icon = "fa-trash",
  color = ifelse(spam > 10, "warning", "primary")
)
```    

### Construction Arisings

```{r}
spam = computeSpam()
valueBox(
  spam, icon = "fa-trash",
  color = ifelse(spam > 10, "warning", "primary")
)
```    

Column {style="height:100pc;"}
-----------------------------------------------------------------------

### WfH Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

### Municipal Waste Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

### Packaging Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

Column {style="height:100pc;"}
-----------------------------------------------------------------------

### WfH Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

### Municipal Waste Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

### Packaging Recycling

```{r}
spam = computeSpam()
renderGauge({
  gauge(spam, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
  ))
})
```    

Resource Productivity
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}
# Unit dropdown
selectInput(inputId = "indicator", label = "Select the unit you would like to see the data in:",
  c("Kilotonnes" = "Absolute",
  "Tonnes per capita" = "Per_capita",
  "kg per £ GBP" = "Productivity"))

# Input data to paramaterise slider bar 
RMC <- read_excel("data.xlsx", sheet = "RMC") %>% 
  gather(Type, Quantity, - Date)

# Set upper and lower bound for the slider
minvalue <- floor(min(RMC$Date, na.rm = TRUE))
maxvalue <- ceiling(max(RMC$Date, na.rm = TRUE))

# Create slider
sliderInput("Year", 
            label = "Select the range of years you are interested in:",
            min = minvalue, max = maxvalue, value = c(minvalue, maxvalue), sep = "")
```
\
 
**Definition**: Raw material consumption (RMC) represents the world-wide amount of primary raw materials directly and indirectly used by our economy. In other words, it represents the portion of annual global raw material extraction attributable to final use.
&nbsp;  

\

**Data Sources:** 
\
[Owen, A., Giesekam, J., Barrett, J. (2020) Material footprint and resource efficiency in the UK](http://sciencesearch.defra.gov.uk/Default.aspx?Menu=Menu&Module=More&Location=None&ProjectID=20306&FromSearch=Y&Publisher=1&SearchText=ev0279&SortString=ProjectCode&SortOrder=Asc&Paging=10%20-%20Description)

Row
-----------------------------------------------------------------------

### Raw Material Consumption

```{r, fig.width=10, fig.height=4, dpi=300}
target <- c("Ore_Materials", "Biomass_Materials", "Fossil_Fuels", "NMMM", "Material_Footprint")
target2 <- c("Ores.p.c", "BiomassMaterials.p.c", "FossilFuels.p.c", "Minerals.p.c", "Material_Footprint.p.c")
target3 <- c("Oresrp", "BiomassMaterialsrp", "FossilFuelsrp", "Mineralsrp", "Material_Footprintrp")

RMC2 <- 
  read_excel("data.xlsx", sheet = "RMC") %>% 
  gather(Type, Quantity, - Date) %>% filter (Type %in% target) 

RMCpop <- 
  read_excel("data.xlsx", sheet = "RMC") %>%
  mutate(Ores.p.c = (Ore_Materials*1000)/Population) %>%
  mutate(BiomassMaterials.p.c = (Biomass_Materials*1000)/Population) %>%
  mutate(FossilFuels.p.c = (Fossil_Fuels*1000)/Population) %>%
  mutate(Minerals.p.c = (NMMM*1000)/Population) %>%
  mutate(Material_Footprint.p.c = (Material_Footprint*1000)/Population) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% target2) 

RMCrp <- 
  read_excel("data.xlsx", sheet = "RMC") %>%
  mutate(Oresrp = GDP/(Ore_Materials*1000000)) %>%
  mutate(BiomassMaterialsrp = GDP/(Biomass_Materials*1000000)) %>%
  mutate(FossilFuelsrp = GDP/(Fossil_Fuels*1000000)) %>%
  mutate(Mineralsrp = GDP/(NMMM*1000000)) %>% 
  mutate(Material_Footprintrp = GDP/(Material_Footprint*1000000)) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% target3) 

getDataset <- reactive({
   ant <- if (input$indicator=="Absolute")
    {
      return(RMC2) %>% filter(RMC2$Date >= input$Year[1]  &
             RMC2$Date <= input$Year[2])
    }
    else if (input$indicator=="Per_capita")
    {
      return(RMCpop) %>% filter(RMCpop$Date >= input$Year[1]  &
             RMCpop$Date <= input$Year[2])
    }
    else
    {
      return(RMCrp) %>% filter(RMCrp$Date >= input$Year[1]  &
             RMCrp$Date <= input$Year[2])
    }
   
  })

RMCchart <- renderPlotly({
  ggplotRMC <- ggplot(getDataset(), aes(x= Date, y = Quantity, group = Type)) +
  geom_line(aes(color=Type)) +
  scale_x_continuous(breaks=seq(minvalue, maxvalue, 1)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
  plotlyRMC <- ggplotly(ggplotRMC) %>% 
  layout(legend = list(orientation = 'h')) %>% 
  layout(legend = list(x = 0, y = - 0.1)) %>%
  style(hoverinfo = 'none') 
  
}) 

RMCchart
  
```

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, fig.width=10, fig.height=4}
RMCwide <- pivot_wider(RMC2, names_from = Type, values_from = Quantity) 

RMCpopwide <- pivot_wider(RMCpop, names_from = Type, values_from = Quantity) %>% as.data.frame(RMCpopwide) %>% mutate_if(is.numeric, round, digits=2) 

view(RMCpopwide)

RMCrpwide <- pivot_wider(RMCrp, names_from = Type, values_from = Quantity) %>% as.data.frame(RMCrpwide) %>% mutate_if(is.numeric, round, digits=2)

ddata <- reactive({
    if (input$indicator=="Absolute")
    {
      return(RMCwide) %>% filter(RMCwide$Date >= input$Year[1]  &
             RMCwide$Date <= input$Year[2])
    }
    else if (input$indicator=="Per_capita") 
    {
      return(RMCpopwide) %>% filter(RMCpopwide$Date >= input$Year[1]  &
             RMCpopwide$Date <= input$Year[2])
    }
    else
    {
      return(RMCrpwide) %>% filter(RMCrpwide$Date >= input$Year[1]  &
             RMCrpwide$Date <= input$Year[2])
    }
  })

renderDT(
          ddata(),
          rownames=FALSE,
          extensions = 'Buttons', options = list(dom = 'Bfrtip',
          buttons = list('csv', 
                         'excel',
                      I('colvis')),
          extensions = 'Responsive',
          pageLength = 5))

```

Carbon Footprint {data-navmenu="Emissions"}
=======================================================================
  
Inputs {.sidebar}
-------------------------------------

```{r}
# Unit dropdown
selectInput(inputId = "indicatorcf", label = "Select the unit you would like to see the data in:",
  c("Kilotonnes CO2e" = "Absolute",
  "Tonnes CO2e per capita" = "Per_capita",
  "kg C02e per £GBP" = "Intensity"))

# Input data to paramaterise slider bar 
cf <- read_excel("data.xlsx", sheet = "CF") %>% 
  gather(Type, Quantity, - Date)

# Set upper and lower bound for the slider
minvaluecf <- floor(min(cf$Date, na.rm = TRUE))
maxvaluecf <- ceiling(max(cf$Date, na.rm = TRUE))

# Create slider
sliderInput("Yearcf", 
            label = "Select the range of years you are interested in:",
            min = minvaluecf, max = maxvaluecf, value = c(minvaluecf, maxvaluecf), sep = "")
```

**Definition:** The ‘carbon footprint’ refers to carbon dioxide (CO2), methane (CH4) and nitrous oxide (N2O) emissions resulting from the consumption spending of households, government and charities in England on goods and services, wherever in the world these arise, and in addition to those emitted directly by households.

**Data Sources:** 
\
[Owen, A., Giesekam, J., Barrett, J. (2020) Material footprint and resource efficiency in the UK](http://sciencesearch.defra.gov.uk/Default.aspx?Menu=Menu&Module=More&Location=None&ProjectID=20306&FromSearch=Y&Publisher=1&SearchText=ev0279&SortString=ProjectCode&SortOrder=Asc&Paging=10%20-%20Description)

Row
-----------------------------------------------------------------------
  
###  Carbon footprint (consumption based greenhouse gas emissions)

```{r}
targetcf <- c("Direct_household_emissions", "Production_emissions_national_consumption", "Emissions_embedded_in_imports", "Total")
targetcfpc <- c("Direct_household_emissions.pc", "Production_emissions_national_consumption.pc", "Emissions_embedded_in_imports.pc", "Total.pc")
targetcfin <- c("Direct_household_emissions.in", "Production_emissions_national_consumption.in", "Emissions_embedded_in_imports.in", "Total.in")

cf2 <- 
  read_excel("data.xlsx", sheet = "CF") %>% 
  gather(Type, Quantity, - Date) %>% filter (Type %in% targetcf) 

cf2pop <- 
  read_excel("data.xlsx", sheet = "CF") %>%
  mutate(Direct_household_emissions.pc = (Direct_household_emissions*1000)/Population) %>%
  mutate(Production_emissions_national_consumption.pc = (Production_emissions_national_consumption*1000)/Population) %>%
  mutate(Emissions_embedded_in_imports.pc = (Emissions_embedded_in_imports*1000)/Population) %>%
  mutate(Total.pc = Total*1000/Population) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% targetcfpc) 

cf2in <- 
  read_excel("data.xlsx", sheet = "CF") %>%
  mutate(Direct_household_emissions.in = (Direct_household_emissions*1000000)/GDP) %>%
  mutate(Production_emissions_national_consumption.in = (Production_emissions_national_consumption*1000000)/GDP) %>%
  mutate(Emissions_embedded_in_imports.in = (Emissions_embedded_in_imports*1000000)/GDP) %>%
  mutate(Total.in = (Total*1000000)/GDP) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% targetcfin) 

getDatasetcf <- reactive({
    if (input$indicatorcf=="Absolute")
    {
      return(cf2) %>% filter(cf2$Date >= input$Yearcf[1]  &
             cf2$Date <= input$Yearcf[2])
    }
    else if (input$indicatorcf=="Per_capita")
    {
      return(cf2pop) %>% filter(cf2pop$Date >= input$Yearcf[1]  &
             cf2pop$Date <= input$Yearcf[2])
    }
    else
    {
      return(cf2in) %>% filter(cf2in$Date >= input$Yearcf[1]  &
             cf2in$Date <= input$Yearcf[2])
    }
  })

cfchart <- renderPlotly({
  ggplotcf <- ggplot(getDatasetcf(), aes(x= Date, y = Quantity, group = Type)) +
  geom_line(aes(color=Type)) +
  scale_x_continuous(breaks=seq(minvaluecf, maxvaluecf, 1)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
  plotlyRMC <- ggplotly(ggplotcf) %>% 
  layout(legend = list(orientation = 'h')) %>% 
  layout(legend = list(x = 0, y = - 0.1)) %>%
  style(hoverinfo = 'none')
  
}) 

cfchart
  
```

Row
-----------------------------------------------------------------------


```{r, echo = FALSE, fig.width=10, fig.height=4}
cfwide <- pivot_wider(cf2, names_from = Type, values_from = Quantity) %>% mutate_if(is.numeric, round, digits=0) 

cfpopwide <- pivot_wider(cf2pop, names_from = Type, values_from = Quantity) %>% as.data.frame(RMCpopwide) %>% mutate_if(is.numeric, round, digits=2) 

view(cfpopwide)
cfinwide <- pivot_wider(cf2in, names_from = Type, values_from = Quantity) %>% as.data.frame(RMCrpwide) %>% mutate_if(is.numeric, round, digits=2)

cftab <- reactive({
    if (input$indicatorcf=="Absolute")
    {
      return(cfwide) %>% filter(cfwide$Date >= input$Yearcf[1]  &
             cfwide$Date <= input$Yearcf[2])
    }
    else if (input$indicatorcf=="Per_capita")
    {
      return(cfpopwide) %>% filter(cfpopwide$Date >= input$Yearcf[1]  &
             cfpopwide$Date <= input$Yearcf[2])
    }
    else
    {
      return(cfinwide) %>% filter(cfinwide$Date >= input$Yearcf[1]  &
             cfinwide$Date <= input$Yearcf[2])
    }
  })

DT::renderDT(
          cftab(),
          rownames=FALSE,
          extensions = 'Buttons', options = list(dom = 'Bfrtip',
          buttons = 
          list('print', list(
          extend = 'collection',
          buttons = c('copy','csv','excel','pdf'),
          text = 'Download',
          extensions = 'Responsive')),
          pageLength = 5))

```


Waste Sector Emissions {data-navmenu="Emissions"}
=======================================================================
  
Inputs {.sidebar}
-------------------------------------

**Unit:** Million tonnes
\  

```{r}
# Input data to paramaterise slider bar 
wse <- read_excel("data.xlsx", sheet = "WSE") %>% 
  gather(Type, Quantity, - Date) %>% mutate_if(is.numeric, round, digits=3) 

# Set upper and lower bound for the slider
minvaluewse <- floor(min(wse$Date, na.rm = TRUE))
maxvaluewse <- ceiling(max(wse$Date, na.rm = TRUE))

# Create slider
sliderInput("Range", 
            label = "Select the range of years you are interested in:",
            min = minvaluewse, max = maxvaluewse, value = c(minvaluewse, maxvaluewse), sep = "")
```

\ 

**Definition**: The ‘waste management sector’ is a category used in international reporting and for which data in collected within the National Atmospheric Emissions Inventory.  Greenhouse gases covered within the inventory are carbon dioxide (CO2), methane (CH4), nitrous oxide (N2O) and fluorinated compounds (hydrofluorocarbons (HFCs), perfluorocarbons (PFCs), sulphur hexafluoride (SF6) and nitrogen trifluoride (NF3).
\ 

**Data Sources:** 
\ 

[Greenhouse Gas Inventories for England, Scotland, Wales & Northern Ireland: 1990-2018](https://naei.beis.gov.uk/reports/reports?section_id=4)

Row
-----------------------------------------------------------------------
  
### Domestic greenhouse gas (GHG) emissions from the Waste Management Sector

```{r}
wse$Type<-factor(wse$Type, levels=c('Anaerobic_Digestion', 'Waste_incineration', 'Composting', 'Waste-water handling', 'Landfill'))

 d <- reactive({
    filtered <-
      wse %>%
      filter(wse$Date >= input$Range[1],
             wse$Date <= input$Range[2])
  })

wsechart <- renderPlotly({
  ggplotwse <- ggplot(d(),
                       aes(fill = Type, x= Date, y= Quantity)) +
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=seq(minvaluewse, maxvaluewse, 2)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
  plotlyRMC <- ggplotly(ggplotwse) %>% 
  layout(legend = list(orientation = 'h')) %>% 
  layout(legend = list(x = 0, y = - 0.1))
  
}) 

wsechart
  
```

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, fig.width=10, fig.height=4}
wsetab <- read_excel("data.xlsx", sheet = "WSE") %>% mutate_if(is.numeric, round, digits=3)

wsetab2 <- reactive({
    filtered <-
      wsetab %>%
      filter(wsetab$Date >= input$Range[1],
             wsetab$Date <= input$Range[2])
  })
 
renderDT(
          wsetab2(),
          rownames=FALSE,
          extensions = 'Buttons', options = list(dom = 'Bfrtip',
          buttons = list('csv', 
                         'excel',
                      I('colvis')),
          extensions = 'Responsive',
          pageLength = 5)) 

```

Waste Sector Emissions Alt {data-navmenu="Emissions"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```

Row
-----------------------------------------------------------------------

### WSEalt

```{r, fig.width=10, fig.height=4}
wseme <- read_excel("data.xlsx", sheet = "WSE") 

dygraph(wseme, main = "WSE") %>% 
  dyRangeSelector(dateWindow = c("2010", "2018"))

```

Row
-----------------------------------------------------------------------
```{r}

```


Total Waste Arisings {data-navmenu="Waste Arisings"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```

Row
-----------------------------------------------------------------------

### Waste arisings

```{r, fig.width=10, fig.height=4}

```

Row
-----------------------------------------------------------------------
```{r}

```

Avoidable Waste {data-navmenu="Waste Arisings"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

Avoidable Plastic Waste {data-navmenu="Waste Arisings"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

Food Waste {data-navmenu="Waste Arisings"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

Residual Waste {data-navmenu="Waste Arisings"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

Row
-----------------------------------------------------------------------

WfH Recycling {data-navmenu="Recycling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

targetwfhrate <- c("Arisings", "Of which recycled (excl. IBAm)", "Of which recycled (incl. IBAm)")

selectInput("wfhanreg", 
              label = "Select your region of interest", 
              c("UK" = "UK",
                        "England" = "England",
                        "Norther Ireland" = "NI",
                        "Scotland" = "Scotland",
                        "Wales" = "Wales"))

selectInput("wfhaniba", 
              label = "Include/Exclude IBA", 
              c("Include IBA" = "Include IBA",
                "Exclude IBA" = "Exclude IBA"))

wfhinput <- read_excel("data.xlsx", sheet = "WFHan") %>%
  gather(Region, Quantity, -Measure, -Date)

# Set upper and lower bound for the slider
minvaluewfh <- floor(min(wfhinput$Date, na.rm = TRUE))
maxvaluewfh <- ceiling(max(wfhinput$Date, na.rm = TRUE))

# Create slider
sliderInput("Range", 
            label = "Select the range of years you are interested in:",
            min = minvaluewfh, max = maxvaluewfh, value = c(minvaluewfh, maxvaluewfh), sep = "")

wfhrate <- wfhinput %>% filter (Measure %in% targetwfhrate) 

wfhpop <- 
  wfhrate %>%
  mutate(Ores.p.c = (Ore_Materials*1000)/Population) %>%
  mutate(BiomassMaterials.p.c = (Biomass_Materials*1000)/Population) %>%
  mutate(FossilFuels.p.c = (Fossil_Fuels*1000)/Population) %>%
  mutate(Minerals.p.c = (NMMM*1000)/Population) %>%
  mutate(Material_Footprint.p.c = (Material_Footprint*1000)/Population) %>%
  gather(Type, Quantity, - Date) %>% filter (Type %in% target2) 

getDataset <- reactive({
   ant <- if (input$indicator=="Absolute")
    {
      return(RMC2) %>% filter(RMC2$Date >= input$Year[1]  &
             RMC2$Date <= input$Year[2])
    }
    else if (input$indicator=="Per_capita")
    {
      return(RMCpop) %>% filter(RMCpop$Date >= input$Year[1]  &
             RMCpop$Date <= input$Year[2])
    }
    else
    {
      return(RMCrp) %>% filter(RMCrp$Date >= input$Year[1]  &
             RMCrp$Date <= input$Year[2])
    }
   
  })


RMCchart <- renderPlotly({
  ggplotRMC <- ggplot(getDataset(), aes(x= Date, y = Quantity, group = Type)) +
  geom_line(aes(color=Type)) +
  scale_x_continuous(breaks=seq(minvalue, maxvalue, 1)) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank())
  
  plotlyRMC <- ggplotly(ggplotRMC) %>% 
  layout(legend = list(orientation = 'h')) %>% 
  layout(legend = list(x = 0, y = - 0.1)) %>%
  style(hoverinfo = 'none') 
  
}) 

RMCchart


```

\ 

**Definition**: ‘Waste from Households’ recycled refers to waste generated by households sent for recycling, composting or reuse in England. This measure is calculated in accordance with Waste Framework Directive (2008/98/EC) and includes waste from regular household collection, civic amenity sites, bulky waste and other household waste.

\ 

**Data Sources:** 
\ 

[Defra (2020) Local authority collected waste management - annual results](https://www.gov.uk/government/statistics/local-authority-collected-waste-management-annual-results)
 
Row  {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Tonnages

```{r}

```

### Rate
    
```{r}

```

Row
-----------------------------------------------------------------------


Municipal Waste Recycling {data-navmenu="Recycling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

wfhan <- read_excel("data.xlsx", sheet = "WFHan") %>%
  gather(Region, Value,- Measure, - Year) 

```

C&I Waste Recycling {data-navmenu="Recycling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

C & D Waste Recovery {data-navmenu="Recycling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```

Row
-----------------------------------------------------------------------

```{r}

```

Packaging Waste Recycling {data-navmenu="Recycling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

```
Row
-----------------------------------------------------------------------

```{r}

```
Row
-----------------------------------------------------------------------

Row
-----------------------------------------------------------------------

Municipal Waste Landfilled {data-navmenu="Landfilling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```
Row
-----------------------------------------------------------------------
```{r}

```

Biodegradable Waste Landfilled {data-navmenu="Landfilling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```

Row
-----------------------------------------------------------------------
```{r}

```

Food Waste Landfilled {data-navmenu="Landfilling"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```
Row
-----------------------------------------------------------------------

```{r}

```
Row
-----------------------------------------------------------------------

Row
-----------------------------------------------------------------------

Illegal Waste Sites {data-navmenu="Waste Crime"}
=======================================================================

Inputs {.sidebar}
-------------------------------------
```{r}

```
Row
-----------------------------------------------------------------------
```{r}

```

Fly-tipping {data-navmenu="Waste Crime"} 
=======================================================================
Inputs {.sidebar}
-------------------------------------
```{r}

```
Row
-----------------------------------------------------------------------
```{r}

```

Litter {data-navmenu="Waste Crime"}
=======================================================================
Inputs {.sidebar}
-------------------------------------
```{r}

```
Row
-----------------------------------------------------------------------
```{r}

```

Row
-----------------------------------------------------------------------

Row
-----------------------------------------------------------------------

Circular Economy
=======================================================================
  
Row
-----------------------------------------------------------------------
  
### Material Flows
```{r}

# Load data
linkages2 <- read_xlsx("SankeyData2.xlsx", "links")
noders2  <- read_xlsx("SankeyData2.xlsx", "nodes")

# Sankey plot it
sankey <- sankeyNetwork(Links = linkages2, Nodes = noders2, Source = "source", Target = "target", Value = "value", NodeID = "name", fontSize = 12, nodeWidth = 60, iteration = 1)

sankey
```



